---
title: "RMD Template"
author: 
  - Foo Bar^[baz, affiliation]
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  # - \usepackage{setspace}\doublespacing
  - \usepackage{amsmath}
editor_options:
  chunk_output_type: console
output: 
  # bookdown::html_document2
  bookdown::pdf_document2
  # bookdown::word_document2
bibliography: bibliography.bib
link-citations: yes
toc: no
urlcolor: blue
---

```{r r-setup, include=FALSE}
## knitr options
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(results = 'hide')
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.align = 'center')

## R options
options(digits=3)

require(datzen)
require(dplyr)
```

check out [markdown syntax](https://rmarkdown.rstudio.com/authoring_pandoc_markdown.html)

# Intro: What to do and Why

Computations done in R [@rstats] .

Following methods of `[@ref2_temp]` .

* blah 
  + blah blah
  


## Manual Pandoc Tables

See the table \@ref(tab:table-syntax)

|       | One | Two   |
|-------|-----|-------|
| row 1 | `f(...)` | $f(.)$ |
| row 2 | code  | latex  |

Table: (\#tab:table-syntax) Foo Caption

## knitr table to structure easier

See the table \@ref(tab:table-function)

```{r table-function, results='asis',echo=FALSE}

out = cbind(
c('predict(brms(...,sample_prior="only"))',
  'predict(brms(...,sample_prior=FALSE))'),
c('brms(...,sample_prior=FALSE)'))

rownames(out) = c('prior','posterior')
colnames(out) = c('Predictive (LHS Outcome)','Parameter (RHS Component)')

knitr::kable(out,
             format='latex',
             align='c',
             booktabs=TRUE,
             caption = 'Function Analogues of Distributions')
```

## Alignment in equation blocks

results in formula \@ref(eq:fay-herriot) below



\begin{equation}
\begin{aligned}
Y &\sim MVN(\theta X, \epsilon I) \\
\theta_p &\sim N(\mu_p,1) \forall p \in 1,\ldots,P \\
\epsilon &\sim Normal(0,\sigma)\\
\sigma &\sim t(3, 0, 10)
\end{aligned}
(\#eq:fay-herriot)
\end{equation}





```{r setup-ex-reg, results='asis'}
seed_pick = 123

dat_real = iris

dat_temp = dat_real %>% 
  distinct(.,Species,.keep_all = TRUE)

formula_spec = Sepal.Length ~ -1 + Sepal.Width + Petal.Length + Petal.Width + Species

```

# Section 2


## Reference Knitr Tables

```{r table-knitr-1, results="asis",echo=FALSE}


out_1 = head(iris)

row.names(out_1) = letters[1:(nrow(out_1))]

knitr::kable(out_1,
booktabs = TRUE,
caption = 'A Table of Blah Blah')

```

As desired, the second row of Table \@ref(tab:table-knitr-1) shows that blah blah blah. In the next section, we will see bloop bloop bloop.

## Reference Figures

Comparing table \@ref(tab:table-knitr-1) with table \@ref(tab:table-knitr-2) we see that blah blah blah. The bloop bloop bloop.


```{r table-knitr-2, results="asis"}

out_2 = rbind(t(head(iris)),
            t(head(iris))
            )

row.names(out_2) = letters[1:(nrow(out))]

knitr::kable(out,
booktabs = TRUE,
caption = 'A Table of Bloop Bloop')

```

To reference tables in the appendix, see appendix table \@ref(tab:table-knitr-fake)

Making reference to Figure \@ref(fig:fig-hist-iris) maps to the chunk name

```{r fig-hist-iris,fig.cap="histogram for iris"}
hist(iris$Sepal.Length)
```

# Discussion: We did this and showed that, maybe try out

We did this and showed that.


# Appendix

## A

We purposely compare two fake datasets here in the appendix.


```{r setup-ex-fake}

y_fake_1 = rnorm(-100,n=nrow(dat_temp))
dat_fake_1 = cbind(Sepal.Length=y_fake_1,dat_temp[,-1])

y_fake_2 = rnorm(100,n=nrow(dat_temp))
dat_fake_2 = cbind(Sepal.Length=y_fake_2,dat_temp[,-1])


```

```{r table-knitr-fake, results='markup'}
out_temp = rbind(head(dat_fake1,
                      head(dat_fake2)
                      )
                 )
knitr::kable(out_temp)
```


```
place bibliography.bib file in same directory, leave # References section blank 
```
# References
